Assessing exposure to Atlantic Basin tropical storms in United States counties

### 2016-07-20 writing/DraftExposurePaper/DraftExposurePaper.Rmd
precipitation lag plot

@@

distance_2000$value <- cut(distance_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")

@@

rain_2000$value <- cut(rain_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")

@@

```{r echo = FALSE}
#TS winds and above
TS_wind_exposure <- county_wind(counties = my_fips,
                             start_year = 1988,
                             end_year = 2011,
                             wind_limit = 18,
                             wind_var = "max_sust")
#HU exposures (32.1 mps and above)
HU_wind_exposure <- county_wind(counties = my_fips,
                                start_year = 1988,
                                end_year = 2011,
                                wind_limit = 32.1,
                                wind_var = "max_sust")
TS_wind_2000 <- TS_wind_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) # Max count of 178 is a NA value
TS_wind_2000 <- subset(TS_wind_2000, !is.na(TS_wind_2000$region)) # Remove NA observation
HU_wind_2000 <- HU_wind_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) # Max of 1 again for hits for top Storm-
                                                                       # County pairs
TS_wind_2000$value <- cut(TS_wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_TS_2000 <- CountyChoropleth$new(TS_wind_2000)
map_TS_2000$set_zoom(eastern_states)
map_TS_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_TS_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor TS Wind Metric"
a <- map_TS_2000$render()
HU_wind_2000$value <- cut(HU_wind_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
map_HU_2000 <- CountyChoropleth$new(HU_wind_2000)
map_HU_2000$set_zoom(eastern_states)
map_HU_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_HU_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor HU Wind Metric"
b <- map_HU_2000$render()
```

@@

```{r}
#Category 3 and above 
cat3_exposure <- county_wind(counties = my_fips,
                                start_year = 1988,
                                end_year = 2011,
                                wind_limit = 50,
                                wind_var = "max_sust")
cat3_2000 <- cat3_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
cat3_2000$value <- cut(cat3_2000$count, c(0, 1, 2, 3, 4, 5, 6, 7), 
                   labels = c("1", "2", "3", "4", "5", "6", "7"), 
                   include.lowest = TRUE)
map_cat3_2000 <- CountyChoropleth$new(cat3_2000)
map_cat3_2000$set_zoom(eastern_states)
map_cat3_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_cat3_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Category 3 and Above Wind Metric"
c <- map_cat3_2000$render()
```

@@

JMF-- I do not think that using the top 2000 Storm-County pairs will be too descriptive (All 3 maps have the identical 2000 pairs), any ideas?

@@

```{r echo = FALSE}
exposure_name <- c("Rain_Exposure", "Distance_Exposure")
count <- c(sum(rain_count$count), sum(distance_count$count))
exposure_table <- cbind(exposure_name, count)
exposure_table <- data.frame(exposure_table)
exposure_table %>%
        mutate(exposure_name = gsub("_", " ", exposure_name)) %>%
        kable(col.names = c("Exposure Criteria", "Total # exposed counties"), 
              caption = "Total number of county hits based on rain, distance, and wind exposures")
```
```{r}
rain_exposure$county_storm <- transmute(rain_exposure, county_storm = paste0(fips, " ", storm_id))
distance_exposure$county_storm <- transmute(distance_exposure, county_storm = paste0(fips, " ", storm_id))
all_exposure <- full_join(rain_exposure, distance_exposure, by = "county_storm")
both_exposure <- subset(all_exposure, tot_precip >= 75 & storm_dist.x <= 100) #4040 observations
rain_only <- subset(all_exposure, tot_precip >= 75 & storm_dist.x > 100) #4200 obs
distance_only <- subset(all_exposure, tot_precip < 75 & storm_dist.x <= 100) #0 obs
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE)
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x > 100, na.rm = TRUE)
sum(all_exposure$tot_precip < 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE) # It appears that in all county-
                                                                                   # storm pairs, there is ample
                                                                                   # rain to meet criteria        
sum(all_exposure$tot_precip < 75, na.rm = TRUE) # This also returns 0
```

>>>>

```{r}
data(closest_dist)

# Generate a list of unique study fips (all in the eastern US)
my_fips <- closest_dist$fips
my_fips <- unique(my_fips)
storm_lag <- county_rain(counties = my_fips,
                             start_year = 1988, end_year = 2011,
                             rain_limit = 150, dist_limit = 500,
                             days_include = -3:3)
storm_lag <- storm_lag %>%
        mutate(storm_county = paste0(storm_id, "_", fips))
data(rain)
rain_lag <- rain %>%
        mutate(storm_county = paste0(storm_id, "_", fips)) %>%
        filter(storm_county %in% storm_lag$storm_county)
rain_lag_plot <- 
```

@@

distance_2000$value <- cut(distance_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

rain_2000$value <- cut(rain_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")

@@

```{r echo = FALSE}
#TS winds and above
TS_wind_exposure <- county_wind(counties = my_fips,
                             start_year = 1988,
                             end_year = 2011,
                             wind_limit = 18,
                             wind_var = "max_sust")
#HU exposures (32.1 mps and above)
HU_wind_exposure <- county_wind(counties = my_fips,
                                start_year = 1988,
                                end_year = 2011,
                                wind_limit = 32.1,
                                wind_var = "max_sust")
TS_wind_2000 <- TS_wind_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) # Max count of 178 is a NA value
TS_wind_2000 <- subset(TS_wind_2000, !is.na(TS_wind_2000$region)) # Remove NA observation
HU_wind_2000 <- HU_wind_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count)) # Max of 1 again for hits for top Storm-
                                                                       # County pairs
TS_wind_2000$value <- cut(TS_wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
exposure_palette <- brewer.pal(8, name = "YlGnBu")
map_TS_2000 <- CountyChoropleth$new(TS_wind_2000)
map_TS_2000$set_zoom(eastern_states)
map_TS_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_TS_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor TS Wind Metric"
a <- map_TS_2000$render()
HU_wind_2000$value <- cut(HU_wind_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
map_HU_2000 <- CountyChoropleth$new(HU_wind_2000)
map_HU_2000$set_zoom(eastern_states)
map_HU_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_HU_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor HU Wind Metric"
b <- map_HU_2000$render()
```

@@

```{r}
#Category 3 and above 
cat3_exposure <- county_wind(counties = my_fips,
                                start_year = 1988,
                                end_year = 2011,
                                wind_limit = 50,
                                wind_var = "max_sust")
cat3_2000 <- cat3_exposure %>% 
        arrange(desc(max_sust)) %>%
        slice (1:2000) %>%
        group_by(fips) %>%
        summarise(count = n()) %>%
        rename(region = fips) %>%
        mutate(region = as.numeric(region), count = as.numeric(count))
cat3_2000$value <- cut(cat3_2000$count, c(0, 1, 3, 5, 7, 9, 11, 13, 15), 
                   labels = c("0-1", "2-3", "4-5", "6-7", "8-9", "10-11", "12-13", "14-15"), 
                   include.lowest = TRUE)
map_cat3_2000 <- CountyChoropleth$new(cat3_2000)
map_cat3_2000$set_zoom(eastern_states)
map_cat3_2000$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_cat3_2000$title <- "Hits for top 2,000 Storm-County Pairs\nfor Category 3 and Above Wind Metric"
c <- map_cat3_2000$render()
```

@@

@@

```{r}
wind_count <- TS_wind_exposure %>%
              group_by(fips) %>%
              summarise(count = n()) %>%
              rename(region = fips) %>%
              mutate(region = as.numeric(region), count = as.numeric(count)) #Same size df as before (only 474 obs)
wind_count$value <- cut(wind_count$count, c(0, 5, 8, 12, 15,
                                                    18, 21, 24),
                           labels = c("0-5", "6-8", "9-12", "13-15",
                                      "16-18", "19-21", "22-24"),
                           include.lowest = TRUE)
exposure_palette <- brewer.pal(7, name = "YlGnBu")

map_wind_count <- CountyChoropleth$new(wind_count)
map_wind_count$set_zoom(eastern_states)
map_wind_count$ggplot_scale <- scale_fill_manual(name = "Hits per\nCounty",
                                                values = exposure_palette,
                                                na.value = "white")
map_wind_count$title <- "Hits for top 2,000 Storm-County Pairs\nfor Wind > 18 m/s"
c <- map_wind_count$render()
```

```{r echo = FALSE}
exposure_name <- c("Distance_Exposure", "Rain_Exposure", "Wind_Exposure")
count <- c(sum(distance_count$count), sum(rain_count$count), sum(wind_count$count))
exposure_table <- cbind(exposure_name, count)
exposure_table <- data.frame(exposure_table)
exposure_table %>%
        mutate(exposure_name = gsub("_", " ", exposure_name)) %>%
        kable(col.names = c("Exposure Criteria", "Total # exposed counties"), 
              caption = "Total number of county hits based on rain, distance, and wind exposures")
```

```{r}
rain_exposure$county_storm <- transmute(rain_exposure, county_storm = paste0(fips, " ", storm_id))
distance_exposure$county_storm <- transmute(distance_exposure, county_storm = paste0(fips, " ", storm_id))
all_exposure <- full_join(rain_exposure, distance_exposure, by = "county_storm")
both_exposure <- subset(all_exposure, tot_precip >= 75 & storm_dist.x <= 100) #4040 observations
rain_only <- subset(all_exposure, tot_precip >= 75 & storm_dist.x > 100) #4200 obs
distance_only <- subset(all_exposure, tot_precip < 75 & storm_dist.x <= 100) #0 obs
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE)
sum(all_exposure$tot_precip >= 75 & all_exposure$storm_dist.x > 100, na.rm = TRUE)
sum(all_exposure$tot_precip < 75 & all_exposure$storm_dist.x <= 100, na.rm = TRUE) # It appears that in all county-
                                                                                   # storm pairs, there is ample
                                                                                   # rain to meet criteria        
sum(all_exposure$tot_precip < 75, na.rm = TRUE) # This also returns 0
```
